Lab 5: Optimization: Answers

### 2023-02-17 Lab 5  Optim/Lab5_Optim.Rmd
Add files via upload

```{r, include = TRUE, message = FALSE, warning = FALSE,fig.width=11, fig.height=5}
#first generate our data (remember to set the seed)
set.seed(123)
x <- rpois(100, 5) #sample from a poisson
xbar <- mean(x) #mean of the poisson samples
n <- length(x) #n obs

>>>>

```{r, include = TRUE, message = FALSE, warning = FALSE,fig.width=11, fig.height=5}
#first generate our data (remember to set the seed)
set.seed(1017)
x <- rpois(100, 5) #sample from a poisson
xbar <- mean(x) #mean of the poisson samples
n <- length(x) #n obs

### 2023-02-17 Lab 5  Optim/Lab5_Optim_AnswerKey.Rmd
Add files via upload

#first generate our data (remember to set the seed)
set.seed(123)
x <- rpois(100, 5) #sample from a poisson
xbar <- mean(x) #mean of the poisson samples
n <- length(x) #n obs

>>>>

#first generate our data (remember to set the seed)
set.seed(1017)
x <- rpois(100, 5) #sample from a poisson
xbar <- mean(x) #mean of the poisson samples
n <- length(x) #n obs
